Preprocessing

### 2023-09-14 analysis/preprocessing.Rmd
Harmonized fields

```{r}
d_journals <- d_journals %>%
  mutate(name_harmonized = case_when(
    name %in% commentaries ~ "Commentary",
    name %in% letters ~ "Letters",
    name %in% other ~ "Other"
  ))
```

@@

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = as.logical(fct_recode(journal_empirical, T = "Yes", F = "No")),
         has_ppc = fct_recode(anyPPC, 
                             "ARCHIVE" = "ARCHIVE ONLY", 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field, jif)
```
#Reclassify PPC name in JOURNAL OF CLINICAL PSYCHIATRY due to quotation marks in raw data name impeding inclusion above

>>>>

```{r}
d_journals <- d_journals %>%
  mutate(name_harmonized = case_when(
    name %in% commentaries ~ "Commentary",
    name %in% letters ~ "Letters",
    name %in% other ~ "Other"
  ))
```
# Harmonize field names deferring to WoS category
```{r}

d_journals <- d_journals %>% 
  mutate(field_harmonized = case_when(
           field == "Psychology | Sport" ~ "Sport",
           field == "Psychology, Applied" ~ "Applied",
           field == "PSYCHOLOGY, APPLIED" ~ "Applied",
           field == "Psychology, Biological" ~ "Biological",
           field == "PSYCHOLOGY, BIOLOGICAL" ~ "Biological",
           field == "Psychology, Clinical" ~ "Clinical",
           field == "PSYCHOLOGY, CLINICAL" ~ "Clinical",
           field == "Psychology, Development" ~ "Developmental",
           field == "PSYCHOLOGY, DEVELOPMENTAL" ~ "Developmental",
           field == "Psychology, Educational" ~ "Educational",
           field == "PSYCHOLOGY, EDUCATIONAL" ~ "Educational",
           field == "Psychology, Experimental" ~ "Experimental",
           field == "PSYCHOLOGY, EXPERIMENTAL" ~ "Experimental",
           field == "Psychology, Mathematical" ~ "Mathematical",
           field == "Psychology, Multidisciplinary" ~ "Multidisciplinary",
           field == "PSYCHOLOGY, MULTIDISCIPLINARY" ~ "Multidisciplinary",
           field == "Psychology, Social" ~ "Social",
           field == "PSYCHOLOGY, SOCIAL" ~ "Social",
           field == "Psychology" ~ "General",
           field == "PSYCHOLOGY - SCIE" ~ "General",
           TRUE ~ field
         ))

@@

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = as.logical(fct_recode(journal_empirical, T = "Yes", F = "No")),
         has_ppc = fct_recode(anyPPC, 
                             "ARCHIVE" = "ARCHIVE ONLY", 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field = field_harmonized, jif)
```
#Reclassify PPC name in JOURNAL OF CLINICAL PSYCHIATRY due to quotation marks in raw data name impeding inclusion above
